Supporting Information

### 2018-03-13 SupportingInformation.Rmd
filled in cross ref, citations thing

output: 
  pdf_document:
    number_sections: yes
    keep_tex: yes
    fig_caption: yes
tables: True
---

@@

<!--New latex commands-->
\newcommand{\mean}{\operatorname{mean}}
\newcommand{\var}{\operatorname{var}}
\newcommand{\cor}{\operatorname{cor}}
\newcommand{\Ps}{\operatorname{P}}
\newcommand{\Dt}{\text{D}^2}

@@

# Descriptions of data
<!--Each data contributor writes one to a few paragraphs about their data.-->

## Soil C and N data

<!--The raw data look like this:-->
```{r load_data_Loecke, echo=F, fig.cap="Plot of the raw soil C and N data.\\label{fig_soilCNraw}", fig.height=5, fig.width=5}
d<-readRDS("Data/RaCA_soilorganicC_soiltotalN_stocks100cm.RDS")
d<-d[,c("SOCstock100","TSNstock100")]
plot(d[,1],d[,2],type="p",col="red",xlab="Soil C",ylab="Soil N",cex.lab=1)
```

<!--The copula looks like this:-->
```{r rankandplot_Loecke, echo=F, fig.cap="Copula plot of soil C and N data. Obtained by applying ranks separately to the C and N data, and then dividing the ranks by $n+1$ where $n$ is the number of sampling locations (see YYY).\\label{fig_soilCNcop}",  fig.height=5, fig.width=5}
#convert to a copula and plot
v_CN<-getcopula(d=d,rankon=T,ploton=T) 
```

<!--Shya please insert an automatic reference to the methods section "Model selection approach" at the location YYY above. I could not easily find a way to do section references by number that was consistent with the figure and table reference system you already have, but perhaps I missed it. In the end I think we will need to be able to refer to sections as well as figures and tables by number. I can see there is a package called "bookdown" that may help but there may be something easier using similar tools to what you have already used for figures and tables.-->

Carbon and nitrogen in soil at many locations across CONUS (Terry to augment this description). The raw data are shown in Figure \ref{fig_soilCNraw}. The copula is shown in \ref{fig_soilCNcop}.

<!--Shyamolina, let's not put in newpages and other spacing modifications until possibly at the end, once all the content is essentially settled-->

## Aphid data
   * Aphid data contains 3 measurements [count, firstflight, flight-duration] at 11 locations for 20 species and for 35 years.
   * We threw out all locations that had fewer than 30 years data 
   * We use species=10 [Name : "Green spruce aphid"] for aphid-count data 
   * We use species=11 [Name : "Leaf-curling plum aphid"] for aphid-firstflight data

## North Sea plankton data
   * Plankton North sea dataset collects data at 26 locations for 22 species and for 56 years.
   * We threw out all locations that had fewer than 45 years data
   * We use species=16 [Name : "Ceratium_furca"] for Plankton_North_Sea data

@@

## Details of methods

### Model selection approach

@@

The third step of model selection was to fit multiple bivariate copula families to the ranked data $(u_i,v_i)$ via maximum likelihood, using the `BiCopEst` function in `VineCopula`. Families considered (with abbreviations and numeric codes here indicated) included the **N**ormal/Gaussian*{1}*, **C**layton*{3}*, **G**umbel*{4}*, **F**rank*{5}*, **J**oe*{6}*, **BB1***{7}*, **BB6***{8}*, **BB7***{9}*, **BB8***{10}*, **S**urvival **C**layton*{13}*, **S**urvival **G**umbel*{14}*, **S**urvival **J**oe*{16}*, **S**urvival **BB1***{17}*, **S**urvival **BB6***{18}*, **S**urvival **BB7***{19}* and **S**urvival **BB8***{20}* copulas.
Akaike Information Criterion (AIC), Bayesian Information Criterion (BIC) and accompanying model weights ($\text{AIC}_{\text{w}}$, $\text{BIC}_{\text{w}}$) were generated using standard formulas (REF). 
<!--Shya, we here need a reference to the Burnham and Anderson book-->
Descriptions of these copula families can be found in introductory texts on copulas
<!--Shya to please insert references for both the books on copulas we have-->
and in references cited in `VineCopula`. The lower- and upper-tail dependence of the 
best-fitting member of each family was also provided by `BiCopEst`.

@@

Finally, $\text{AIC}_{\text{w}}$ values for all fitted models were used to get
model-averaged lower- and upper-tail dependence values using standard model averaging 
formulas
<!--Shya to add reference to Burnham and Anderson, please-->
; likewise for BIC.

<!--Shya please insert some additional material for multivariate datasets - perhaps
you don't need much because basically you just ran the bivariate analysis on each pair
of locations, but you need to say that and then maybe a few sentences about how 
everything was tallied up after having done that-->

### Non-parametric analysis of tail dependence

![Schematic diagram supporting defintions of nonparametric tail dependence statistics.\label{fig_stat_image}](./stat_image.jpg){ width=30%, height=30% }
<!--Shya, can you please change this figure so it shows u (horizontal) and v (vertical) on the axis labels instead of vi and vj? Often times computer variables do not make good mathematical notation, so I have changed this, I also made changes for similar reasons to other notation elsewhere.-->

Left- and right-tail dependence quantify the extent to which two ranked
variables $u_i$, $v_i$ for $i=1,...,n$ 
(see section REF for defintions of $u_i$ and $v_i$)
<!--Shya pls insert ref to the section immediately above this one-->
are related in the left and right tails, respectively, of their 
distributions (REF). 
<!--Shya, pls cite the Nelson book-->
Our nonparametric study of tail dependence uses three
statistics which can quantify the extent to which $u_i$ and $v_i$ are 
related in any part of their distributions. We here describe the 
statistics. The statistics were formulated with positively associated
variables in mind. All the variables we study are positively associated
when they are significantly associated. So definitions and associated 
diagrams will assume positive associations, though generalizations are 
possible. Given two bounds 
$0 leq l_b < u_b \leq 1$, we define the parallel lines $u+v=2l_b$ and 
$u+v=2u_b$ which intersect the unit square in which the $u_i$ and $v_i$ 
fall (these are the blue and red lines, respectively, in 
Figure \ref{fig_stat_image}). Our statistics quantify the dependence
between $u_i$ and $v_i$ in the region bounded by these lines.
Using $l_b=0$ and some value $u_b\leq 0.5$ can give information about 
dependence in the left parts of the distributions of $u$ and $v$, and 
using $u_b=1$ and $l_b \geq 0.5$ can give information about dependence in 
the right parts of the distributions.

@@

We also defined a statistic $\Ps_{l_b,u_b}$, using the same bounds
$u+v=2l_b$ and $u+v=2u_b$, as follows. For a distance $h$, we defined
$S(h)$ to be the number of points $(u_i,v_i)$ within the bounds 
and a distance less than $h$ from the line $v=u$, divided by the 
total number of points within the bounds. This function is
defined for $h$ going from $0$ to a distance $h_{\text{max}}$ which
is half the longer of the two segments obtained by intersecting the
bounds with the unit square. It is easy to see $S(0)=0$ and 
$S(h_{\text{max}})=1$. We defined $S_i(h)$, for the same range 
of $h$, to be the area within the bounds and the unit square
and within distance $h$ of the line $v=u$, divided by the area
within the bounds and the unit square. This is the expected value of
$S(h)$ for independent data. We then defined
\begin{equation}\label{eq.P}
   P_{l_b,u_b} = \int_0^{h_{max}} ( S(h) - S_i(h) ) dh.
\end{equation}
As for $\cor_{l_b,u_b}$, larger values of $P_{l_b,u_b}$ 
indicate stronger positive association
between $u$ and $v$ in the region given by the bounds.

The third statistic, $\Dt_{l_b,u_b}(u,v)$, is the average squared 
distance between points satisfying $u_i+v_i>2l_b$ and 
$u_i+v_i<2u_b$ and the line $v=u$. Unlike $\cor_{l_b,u_b}$ and 
$\Ps_{l_b,u_b}$, which are large when points satisfying $u_i+v_i>2l_b$ and 
$u_i+v_i<2u_b$ cluster close to the line $v=u$, $\Dt_{l_b,u_b}$ is 
then small. 
Thus large values of $\cor_{l_b,u_b}$ and $\Ps_{l_b,u_b}$ indicate strong 
dependence in the portions of the distributions of $u$ and $v$ given by 
the bounds $u_i+v_i>2l_b$ and $u_i+v_i<2u_b$, whereas small values of 
$\Dt_{l_b,u_b}$ indicate strong dependence.

For large datasets (i.e., datasets with large $n$),
we can consider $l_b$ and $u_b$ close together without incurring undue
sampling variation in our statistics, and we can consider 
several different bands $(l_b,u_b)$ to understand how dependence
varies in different parts of the distributions. But for datasets with 
smaller $n$ we considered only $l_b=0$, $u_b=0.5$ and $l_b=0.5$, $u_b=1$.
We use the shorthand $\cor_l=\cor_{0,0.5}$ ($l$ is for "lower") 
and $\cor_u=\cor_{0.5,1}$ ($u$ is for "upper"); likewise $\Ps_l=\Ps_{0,.5}$,
$\Ps_u=\Ps_{0.5,1}$, $\Dt_l=\Dt_{0,0.5}$, and $\Dt_u=\Dt_{0.5,1}$.

The difference $\cor_l-\cor_u$ is expected to be positive if 
dependence in the left halves of the distributions is stronger 
than dependence in their right halves; likewise for $\Ps_l-\Ps_u$.
This holds, for instance, for the Clayton copula (REF).
<!--Shya to cite the Nelson book-->
The difference $\Dt_u-\Dt_l$, in which the "upper" and
"lower" statistics occur in opposite order, is also expected to be 
positive under the same conditions. We use these three differences
to detect asymmetry of tail dependence. Likewise, for large datasets,
we consider $\cor_{l_b,u_b}-\cor_{1-u_b,1-l_b}$, 
$\Ps_{l_b,u_b}-\Ps_{1-u_b,1-l_b}$ and
$\Dt_{1-u_b,1-l_b}-\Dt_{l_b,u_b}$ with $l_b=0$ and $u_b$ close to $0$.

@@

### Stat-testing of Non-parametric analysis (for limited number of datapoints)

Here, we want to test our $3$ types of nonparametric tail dependent statistics on both small $(35)$ and large $(1000)$ number of datapoints drawn from $4$ types of bivariate copula, namely, *Clayton* , *Normal*, *Frank* and *Survival Clayton*. Whereas *Normal* and *Frank* have symmetric tail dependence, *Clayton* and *Survival Clayton* have lower and upper tail dependence, respectively.
First we chose a set of parameters [using *iRho* from *Copula* package] for each type of copula for which spearman correlation will be $10$ equispaced number in between [$0,0.9$]. Then for each parameter (or spearman value) of each type of copula we carried out $100$ simulation and calculated $(Corl , Coru, Pl, Pu, D2l, D2u)$ stats. We took mean of our statistic $Corl-Coru$, $Pl-Pu$ and $D2u-D2l$ over $100$ simulations and In Figure \ref{fig_stat_testing35}, we plotted those statistic against spearman correlation. We put the standard error bar around each point in the plot and these errors got minimized with increasing numbe of data points [Figure \ref{fig_stat_testing1000}]. Statistic $Corl - Coru$, $Pl-Pu$ and $D2u-D2l$ should be $0$ for spearman=$0$ for *Clayton* and *Survival Clayton* and should remain $0$ for all values of spearman for symmetric copula like *Normal* and *Frank*. To verify this, we executed t-test and report the $p$-values for each case and most of the case shows $p>0.05$.

@@

## Soil C and N data

### Model selection approach
<!--This does the computations for this section-->
```{r bivmodselect_Loecke, echo=F, cache=T, cache.extra=list(seed,v_CN,mtime("OurBiCopSelect.R"),mtime("MyBiCopGofTest.R"))}
set.seed(seed)
families_Loecke<-c(1,3:10,13:14,16:20) 
BivMS_res_Loecke<-OurBiCopSelect(u1=v_CN[,1],u2=v_CN[,2],families=families_Loecke,level=0.05,AICBIC="AIC",numBSsmall=100,pthresh=0.2,numBSlarge=1000,gofnormal=F,status=F)
```

@@

### Non-parametric analysis of tail dependence
<!--Do the intensive part of the analysis, calculating stats on the data and surrogates-->
```{r stat_soilCN_graphic_approach, echo=F, cache=T, cache.extra=list(seed,v_CN,mtime("CopulaFunctions_flexible.R"),mtime("copsurrog2d.R"))}
set.seed(seed)

@@

## Aphid abundance data for 'Green spruce aphid'
<!--Add common and species name to header-->

### Model selection approach

@@

<!--\newpage-->

@@

### Non-paramtric analysis of tail dependence

@@

## Aphid first flight data for 'Leaf-curling plum aphid' 
<!--Add species common name and scientific name to header-->

### Model selection approach

@@

\newpage
```{r tab_ff_AICw, echo=F, results='markup'}
knitr::kable(RES_aphid_ff$info_ord_AICw[,,1], 
             format='pandoc',
             caption = "Aphid_firstflight : AICw for best fit copula family for each selective location pair\\label{tab_ff_AICw}",
             booktabs=TRUE
             )
```

@@

### Non-parametric analysis of tail dependence

@@

## North sea plankton data for 'Ceratium furca'

@@

### Model selection approach

@@

<!--\newpage-->
```{r tab_pns_bestcop, echo=F, results='markup'}
knitr::kable(RES_plankton_north_sea$info_ord_copname[,,1],
             format='pandoc',
             caption = "Plankton_north_sea : Best fit copula family for each selective location pair\\label{tab_pns_bestcop}",
             booktabs=TRUE
             )
```

\newpage
```{r tab_pns_AICw,echo=F,results="markup"}
knitr::kable(RES_plankton_north_sea$info_ord_AICw[,,1],
             format="pandoc",
             digits=3,
             caption = "Plankton_north_sea : AICw for best fit copula family for each selective location pair\\label{tab_pns_AICw}",
             booktabs=TRUE)
```

@@

<!--\newpage-->
```{r tab_pns_p_KS,echo=F,results="markup"}
knitr::kable(RES_plankton_north_sea$gfc_p_KS,
             format="pandoc",
             digits=3,
             caption = "Plankton_north_sea : p-values (Kolmogorov-Smirnov-based test) for lowest AIC based best fit copula\\label{tab_pns_p_KS}",
             booktabs=TRUE)
```

@@

### Non-paramtric analysis of tail dependence
```{r stat_plankton_north_sea, echo=F, cache=T, cache.extra=list(seed,data_plankton_north_sea)}
set.seed(seed)
resloc<-"./Results/stat_results/stat_plankton_north_sea/"

@@

## Aphid count

@@

<!--Shya to add results about skewness of spatial means-->
```{r skewness_count_plot, results='hide', echo=F, cache=T, cache.extra=list(seed,mtime("ncsurrog.R"),mtime("skewness_multivar_dataset.R"))}
set.seed(seed)
pdf("./Results/skewness_results/skewness_aphid_count/skewness_aphid_count_sp_10.pdf")
par(mfrow=c(2,1))
numsurrog<-10000
loclist<-good_loclist(d_allsp=data_aphid_count,sp=10,data_pt_thrs=30)
answer1k<-skewness_testing(ts_matrix=sp_data(sp=10,d_allsp=data_aphid_count),loclist=loclist,numsurrog=numsurrog,ploton=T,
                          corpres="kendall")

@@

## Aphid first flight

@@

<!--Shya to add results about skewness of spatial means-->
```{r skewness_ff_plot, results='hide', echo=F, cache=T, cache.extra=list(seed,mtime("ncsurrog.R"),mtime("skewness_multivar_dataset.R"))}
set.seed(seed)
pdf("./Results/skewness_results/skewness_aphid_ff/skewness_aphid_ff_sp_11.pdf")
par(mfrow=c(2,1))
numsurrog<-10000
loclist<-good_loclist(d_allsp=data_aphid_ff,sp=11,data_pt_thrs=30)

@@

## North Sea plankton

@@

>>>>

output: 
  pdf_document:
    number_sections: yes
    keep_tex: yes
    fig_caption: yes
tables: True

csl: science.csl
bibliography: REF_SI.bib
---

@@

<!--New latex commands-->
\newcommand{\mean}{\operatorname{mean}}
\newcommand{\var}{\operatorname{var}}
\newcommand{\cor}{\operatorname{cor}}
\newcommand{\Ps}{\operatorname{P}}
\newcommand{\Dsq}{\operatorname{D}^2}
<!--\newcommand{\D2}{\operatorname{D}^2} gives error msg : insert $ -->

@@

# Descriptions of data \label{Description_data}
<!--Each data contributor writes one to a few paragraphs about their data.-->

## Soil C and N data  \label{SoilCN_data}

Carbon and nitrogen in soil at many locations across CONUS (Terry to augment this description). The raw data are shown in Figure \ref{fig_soilCNraw}. The copula is shown in Figure \ref{fig_soilCNcop}.

<!--The raw data look like this:-->
```{r load_data_Loecke, echo=F, results='hide'}
#fig.cap="Plot of the raw soil C and N data.\\label{fig_soilCNraw}", fig.height=3, fig.width=3}
d<-readRDS("Data/RaCA_soilorganicC_soiltotalN_stocks100cm.RDS")
d<-d[,c("SOCstock100","TSNstock100")]
pdf("./Results/SoilCNraw.pdf")
plot(d[,1],d[,2],type="p",col="red",xlab="Soil C",ylab="Soil N",cex.lab=1.5,cex.axis=1.5)
dev.off()
```

<!--The copula looks like this:-->
```{r rankandplot_Loecke, echo=F, results='hide'}
#fig.cap="Copula plot of soil C and N data. Obtained by applying ranks separately to the C and N data, and then dividing the ranks by $n+1$ where $n$ is the number of sampling locations (see Sec. \ref{Model_selection}).\\label{fig_soilCNcop}",  fig.height=5, fig.width=5}

#convert to a copula and plot
pdf("./Results/SoilCNcop.pdf")
v_CN<-getcopula(d=d,rankon=T,ploton=T) 
dev.off()
```
<!--Shya please insert an automatic reference to the methods section "Model selection approach" at the location YYY above. I could not easily find a way to do section references by number that was consistent with the figure and table reference system you already have, but perhaps I missed it. In the end I think we will need to be able to refer to sections as well as figures and tables by number. I can see there is a package called "bookdown" that may help but there may be something easier using similar tools to what you have already used for figures and tables.-->
![Plot of the raw soil C and N data.\label{fig_soilCNraw}](./Results/SoilCNraw.pdf){ width=30%, height=30% }

![Copula plot of soil C and N data. Obtained by applying ranks separately to the C and N data, and then dividing the ranks by $n+1$ where $n$ is the number of sampling locations (see Sec. \ref{Model_selection}). \label{fig_soilCNcop}](./Results/SoilCNcop.pdf){ width=30%, height=30% }

## Aphid data \label{Aphid_data}
   * Aphid data contains 3 measurements [count, firstflight, flight-duration] at 11 locations for 20 species and for 35 years.
   * We threw out all locations that had fewer than 30 years data 
   * We use species=10 [Name : "Green spruce aphid"] for aphid-count data 
   * We use species=11 [Name : "Leaf-curling plum aphid"] for aphid-firstflight data

## North Sea plankton data \label{Pns_data}
   * Plankton North sea dataset collects data at 26 locations for 22 species and for 56 years.
   * We threw out all locations that had fewer than 45 years data
   * We use species=16 [Name : "Ceratium_furca"] for Plankton_North_Sea data

@@

## Details of methods \label{Method}

### Model selection approach \label{Model_selection}

@@

The third step of model selection was to fit multiple bivariate copula families to the ranked data $(u_i,v_i)$ via maximum likelihood, using the `BiCopEst` function in `VineCopula`. Families considered (with abbreviations and numeric codes here indicated) included the **N**ormal/Gaussian*{1}*, **C**layton*{3}*, **G**umbel*{4}*, **F**rank*{5}*, **J**oe*{6}*, **BB1***{7}*, **BB6***{8}*, **BB7***{9}*, **BB8***{10}*, **S**urvival **C**layton*{13}*, **S**urvival **G**umbel*{14}*, **S**urvival **J**oe*{16}*, **S**urvival **BB1***{17}*, **S**urvival **BB6***{18}*, **S**urvival **BB7***{19}* and **S**urvival **BB8***{20}* copulas.
Akaike Information Criterion (AIC), Bayesian Information Criterion (BIC) and accompanying model weights ($\text{AIC}_{\text{w}}$, $\text{BIC}_{\text{w}}$) were generated using standard formulas @burnham2003_modelselection. 
<!--Shya, we here need a reference to the Burnham and Anderson book-->
Descriptions of these copula families can be found in introductory texts on copulas @burnham2003_modelselection, @nelsen2007_copula
<!--Shya to please insert references for both the books on copulas we have-->
and in references cited in `VineCopula`. The lower- and upper-tail dependence of the 
best-fitting member of each family was also provided by `BiCopEst`.

@@

Finally, $\text{AIC}_{\text{w}}$ values for all fitted models were used to get
model-averaged lower- and upper-tail dependence values using standard model averaging 
formulas @burnham2003_modelselection
<!--Shya to add reference to Burnham and Anderson, please-->
; likewise for BIC.

<!--Shya please insert some additional material for multivariate datasets - perhaps
you don't need much because basically you just ran the bivariate analysis on each pair
of locations, but you need to say that and then maybe a few sentences about how 
everything was tallied up after having done that ??? -->

### Non-parametric analysis of tail dependence \label{NPA}

<!--Shya, can you please change this figure so it shows u (horizontal) and v (vertical) on the axis labels instead of vi and vj? Often times computer variables do not make good mathematical notation, so I have changed this, I also made changes for similar reasons to other notation elsewhere.-->

Left- and right-tail dependence quantify the extent to which two ranked
variables $u_i$, $v_i$ for $i=1,...,n$ 
(see Sec. \ref{Model_selection} for defintions of $u_i$ and $v_i$)
<!--Shya pls insert ref to the section immediately above this one-->
are related in the left and right tails, respectively, of their 
distributions @nelsen2007_copula. 
<!--Shya, pls cite the Nelson book-->
Our nonparametric study of tail dependence uses three
statistics which can quantify the extent to which $u_i$ and $v_i$ are 
related in any part of their distributions. We here describe the 
statistics. The statistics were formulated with positively associated
variables in mind. All the variables we study are positively associated
when they are significantly associated. So definitions and associated 
diagrams will assume positive associations, though generalizations are 
possible. Given two bounds 
$0 \leq l_b < u_b \leq 1$, we define the parallel lines $u+v=2l_b$ and 
$u+v=2u_b$ which intersect the unit square in which the $u_i$ and $v_i$ 
fall (these are the blue and red lines, respectively, in 
Figure \ref{fig_stat_image}). Our statistics quantify the dependence
between $u_i$ and $v_i$ in the region bounded by these lines.
Using $l_b=0$ and some value $u_b\leq 0.5$ can give information about 
dependence in the left parts of the distributions of $u$ and $v$, and 
using $u_b=1$ and $l_b \geq 0.5$ can give information about dependence in 
the right parts of the distributions.

![Schematic diagram supporting defintions of nonparametric tail dependence statistics.\label{fig_stat_image}](./stat_image.jpg){ width=25%, height=25% }

@@

We also defined a statistic $\Ps_{l_b,u_b}$, using the same bounds
$u+v=2l_b$ and $u+v=2u_b$, as follows. For a distance $h$, we defined
$S(h)$ to be the number of points $(u_i,v_i)$ within the bounds 
and a distance less than $h$ from the line $v=u$, divided by the 
total number of points within the bounds. This function is
defined for $h$ going from $0$ to a distance $h_{\text{max}}$ which
is half the longer of the two segments obtained by intersecting the
bounds with the unit square. It is easy to see $S(0)=0$ and 
$S(h_{\text{max}})=1$. We defined $S_i(h)$, for the same range 
of $h$, to be the area within the bounds and the unit square
and within distance $h$ of the line $v=u$, divided by the area
within the bounds and the unit square. This is the expected value of
$S(h)$ for independent data. We then defined
\begin{equation}\label{eq.P}
   P_{l_b,u_b} = \int_0^{h_{max}} ( S(h) - S_i(h) ) dh.
\end{equation}
As for $\cor_{l_b,u_b}$, larger values of $Ps_{l_b,u_b}$ 
indicate stronger positive association
between $u$ and $v$ in the region given by the bounds.

The third statistic, $\Dsq_{l_b,u_b}(u,v)$, is the average squared 
distance between points satisfying $u_i+v_i>2l_b$ and 
$u_i+v_i<2u_b$ and the line $v=u$. Unlike $\cor_{l_b,u_b}$ and 
$\Ps_{l_b,u_b}$, which are large when points satisfying $u_i+v_i>2l_b$ and 
$u_i+v_i<2u_b$ cluster close to the line $v=u$, $\Dsq_{l_b,u_b}$ is 
then small. 
Thus large values of $\cor_{l_b,u_b}$ and $\Ps_{l_b,u_b}$ indicate strong 
dependence in the portions of the distributions of $u$ and $v$ given by 
the bounds $u_i+v_i>2l_b$ and $u_i+v_i<2u_b$, whereas small values of 
$\Dsq_{l_b,u_b}$ indicate strong dependence.

For large datasets (i.e., datasets with large $n$),
we can consider $l_b$ and $u_b$ close together without incurring undue
sampling variation in our statistics, and we can consider 
several different bands $(l_b,u_b)$ to understand how dependence
varies in different parts of the distributions. But for datasets with 
smaller $n$ we considered only $l_b=0$, $u_b=0.5$ and $l_b=0.5$, $u_b=1$.
We use the shorthand $\cor_l=\cor_{0,0.5}$ ($l$ is for "lower") 
and $\cor_u=\cor_{0.5,1}$ ($u$ is for "upper"); likewise $\Ps_l=\Ps_{0,.5}$,
$\Ps_u=\Ps_{0.5,1}$, $\Dsq_l=\Dsq_{0,0.5}$, and $\Dsq_u=\Dsq_{0.5,1}$.

The difference $\cor_l-\cor_u$ is expected to be positive if 
dependence in the left halves of the distributions is stronger 
than dependence in their right halves; likewise for $\Ps_l-\Ps_u$.
This holds, for instance, for the Clayton copula @nelsen2007_copula.
<!--Shya to cite the Nelson book-->
The difference $\Dsq_u-\Dsq_l$, in which the "upper" and
"lower" statistics occur in opposite order, is also expected to be 
positive under the same conditions. We use these three differences
to detect asymmetry of tail dependence. Likewise, for large datasets,
we consider $\cor_{l_b,u_b}-\cor_{1-u_b,1-l_b}$, 
$\Ps_{l_b,u_b}-\Ps_{1-u_b,1-l_b}$ and
$\Dsq_{1-u_b,1-l_b}-\Dsq_{l_b,u_b}$ with $l_b=0$ and $u_b$ close to $0$.

@@

### Stat-testing of Non-parametric analysis (for limited number of datapoints) \label{Stat_testing}

Here, we want to test our $3$ types of nonparametric tail dependent statistics on both small $(35)$ and large $(1000)$ number of datapoints drawn from $4$ types of bivariate copula, namely, *Clayton* , *Normal*, *Frank* and *Survival Clayton*. Whereas *Normal* and *Frank* have symmetric tail dependence, *Clayton* and *Survival Clayton* have lower and upper tail dependence, respectively.
First we chose a set of parameters [using *iRho* from `Copula` package] for each type of copula for which spearman correlation will be $10$ equispaced number in between [$0,0.9$]. Then for each parameter (or spearman value) of each type of copula we carried out $100$ simulation and calculated $(Corl , Coru, Pl, Pu, D2l, D2u)$ stats. We took mean of our statistic $Corl-Coru$, $Pl-Pu$ and $D2u-D2l$ over $100$ simulations and In Figure \ref{fig_stat_testing35}, we plotted those statistic against spearman correlation. We put the standard error bar around each point in the plot and these errors got minimized with increasing numbe of data points [Figure \ref{fig_stat_testing1000}]. Statistic $Corl - Coru$, $Pl-Pu$ and $D2u-D2l$ should be $0$ for spearman=$0$ for *Clayton* and *Survival Clayton* and should remain $0$ for all values of spearman for symmetric copula like *Normal* and *Frank*. To verify this, we executed t-test and report the $p$-values for each case and most of the case shows $p>0.05$.

@@

## Soil C and N data \label{Ex_SoilCN}

### Model selection approach \label{Ex_SoilCN_Model_selection}
<!--This does the computations for this section-->
```{r bivmodselect_Loecke, echo=F, cache=T, cache.extra=list(seed,v_CN,mtime("OurBiCopSelect.R"),mtime("MyBiCopGofTest.R"))}
set.seed(seed)
families_Loecke<-c(1,3:10,13:14,16:20) 
BivMS_res_Loecke<-OurBiCopSelect(u1=v_CN[,1],u2=v_CN[,2],families=families_Loecke,level=0.05,AICBIC="AIC",numBSsmall=100,pthresh=0.2,numBSlarge=1000,gofnormal=F,status=F)
```

@@

### Non-parametric analysis of tail dependence \label{Ex_SoilCN_NPA}
<!--Do the intensive part of the analysis, calculating stats on the data and surrogates-->
```{r stat_soilCN_graphic_approach, echo=F, cache=T, cache.extra=list(seed,v_CN,mtime("CopulaFunctions_flexible.R"),mtime("copsurrog2d.R"))}
set.seed(seed)

@@

## Aphid abundance data for 'Green spruce aphid' \label{Ex_count}
<!--Add common and species name to header-->

### Model selection approach \label{Ex_count_Model_selection}

@@

@@

### Non-paramtric analysis of tail dependence \label{Ex_count_NPA}

@@

## Aphid first flight data for 'Leaf-curling plum aphid' \label{Ex_ff}
<!--Add species common name and scientific name to header-->

### Model selection approach \label{Ex_ff_Model_selection}

@@

```{r tab_ff_AICw, echo=F, results='markup'}
knitr::kable(RES_aphid_ff$info_ord_AICw[,,1], 
             format='pandoc',
             caption = "Aphid_firstflight : AICw for best fit copula family for each selective location pair\\label{tab_ff_AICw}",
             booktabs=TRUE
             )
```

@@

### Non-parametric analysis of tail dependence  \label{Ex_ff_NPA}

@@

## North sea plankton data for 'Ceratium furca' \label{Ex_pns}

@@

### Model selection approach \label{Ex_pns_Model_selection}

@@

```{r tab_pns_bestcop, echo=F, results='markup'}
knitr::kable(RES_plankton_north_sea$info_ord_copname[,,1],
             format='pandoc',
             caption = "Plankton_north_sea : Best fit copula family for each selective location pair\\label{tab_pns_bestcop}",
             booktabs=TRUE
             )
```

```{r tab_pns_AICw,echo=F,results="markup"}
knitr::kable(RES_plankton_north_sea$info_ord_AICw[,,1],
             format="pandoc",
             digits=3,
             caption = "Plankton_north_sea : AICw for best fit copula family for each selective location pair\\label{tab_pns_AICw}",
             booktabs=TRUE)
```

@@

```{r tab_pns_p_KS,echo=F,results="markup"}
knitr::kable(RES_plankton_north_sea$gfc_p_KS,
             format="pandoc",
             digits=3,
             caption = "Plankton_north_sea : p-values (Kolmogorov-Smirnov-based test) for lowest AIC based best fit copula\\label{tab_pns_p_KS}",
             booktabs=TRUE)
```

@@

### Non-paramtric analysis of tail dependence  \label{Ex_pns_NPA}
```{r stat_plankton_north_sea, echo=F, cache=T, cache.extra=list(seed,data_plankton_north_sea)}
set.seed(seed)
resloc<-"./Results/stat_results/stat_plankton_north_sea/"

@@

## Aphid count \label{skewness_count}

@@

```{r skewness_count_plot, results='hide', echo=F, cache=T, cache.extra=list(seed,mtime("ncsurrog.R"),mtime("skewness_multivar_dataset.R"))}
set.seed(seed)
pdf("./Results/skewness_results/skewness_aphid_count/skewness_aphid_count_sp_10.pdf")
par(mfrow=c(2,1))
numsurrog<-10000
loclist<-good_loclist(d_allsp=data_aphid_count,sp=10,data_pt_thrs=30)
answer1k<-skewness_testing(ts_matrix=sp_data(sp=10,d_allsp=data_aphid_count),loclist=loclist,numsurrog=numsurrog,ploton=T,
                          corpres="kendall")

@@

## Aphid first flight \label{skewness_ff}

@@

```{r skewness_ff_plot, results='hide', echo=F, cache=T, cache.extra=list(seed,mtime("ncsurrog.R"),mtime("skewness_multivar_dataset.R"))}
set.seed(seed)
pdf("./Results/skewness_results/skewness_aphid_ff/skewness_aphid_ff_sp_11.pdf")
par(mfrow=c(2,1))
numsurrog<-10000
loclist<-good_loclist(d_allsp=data_aphid_ff,sp=11,data_pt_thrs=30)

@@

## North Sea plankton \label{skewness_pns}

@@

## References:
